Hydras \& Co.

### 2023-02-20 doc/chap-intro-goedel.tex
small correction in latex document

\chapter{Introduction}

This part contains comments, example  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem.  This work is maintained by Coq community~\cite{CoqCommunity} volunteers: (projects Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}).
The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

>>>>

\chapter{General presentation (draft)}

\section{Introduction}

This part contains comments, examples  and exercises about Russel O'Connor's work on G\"{o}del's first incompleteness theorem  \cite{Godel1986-GDECW}.
O'Connor's work was published in 2005~\cite{OConnor05}, and released as a user-contribution of the \coq proof assistant.
This work is now maintained by Coq community~\cite{CoqCommunity} volunteers and split into two projects: Goedel~\cite{Goedel} and Hydra-battles~\cite{HydraBattles}.

The main reference to this work is  Russel O'Connor's article~\cite{OConnor05}, which we strongly encourage the reader to 
consult regularly.

% ici

\section{The reason behind this work}

  \begin{itemize}
  \item Historical interest on G\"{o}del's proof
  \item Many popularization publications, \emph{e.g.}
    \cite{smullyan1992godel, Hofstadter1999Godel, GoedelCassou}, vs. technical complexity of the full proof .

    \begin{quote}
      The purpose of a proof is \emph{understanding}.
      Efim Zelmanov in~\cite{mathproof}.  
          \end{quote}
        \item O'Connor's proof was written at the end of \coq V7, rewritten at the beginning of \coq V8. Since then, \coq and its ecosystem evolved a lot (new styles, tactics, documentation tools).
          We think this evolution should benefit
          to the original proof-scripts and make their understanding easier.
        \end{itemize}

\section{Historical context}
Russel O'Connor's work is the first computer verified proof 
the essential incompleteness of arithmetic.

\begin{todo}
Reference to previous/later implementations.
\end{todo}
